Clustering exploration for `r params$sample_id`

### 2024-11-14 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
found a few more chunks not to run with test data

- `nbins` is the number of bins for `AddModuleScore` to use. Its default value is 24, which matches Seurat's default value.
```{r }
MSigDB_score <- function(object, category, gs_name, name, nbin = 24) {
  set <- msigdbr(species = "human", category = category)
  set_list <- set %>%
    dplyr::filter(gs_name == gs_name) %>%
    dplyr::distinct(gs_name, gene_symbol, human_ensembl_gene) %>%
    as.data.frame()
  set_list <- list(set_list$human_ensembl_gene)
  suppressWarnings({
    object <- AddModuleScore(object, features = set_list, name = name, nbin = nbin)
  })
  return(object)
}
```

@@

### Cell cycle information
```{r cell_cycle}
s.genes <- srat@assays$RNA@meta.data$gene_ids[srat@assays$RNA@meta.data$gene_symbol %in% cc.genes$s.genes]
g2m.genes <- srat@assays$RNA@meta.data$gene_ids[srat@assays$RNA@meta.data$gene_symbol %in% cc.genes$g2m.genes]
srat <- CellCycleScoring(srat, s.features = s.genes, g2m.features = g2m.genes, set.ident = FALSE, nbin = seurat_nbins)
```

```{r fig.width=20, fig.height=4, out.width='100%'}
visualize_metadata(srat, meta = "Phase", group.by = "seurat_clusters")
```

```{r fig.width=20, fig.height=2.5, out.width='100%'}
visualize_metadata(srat, meta = "S.Score", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "G2M.Score", group.by = "seurat_clusters")
```

@@

```{r fig.height=25, fig.width=20, message=FALSE, warning=FALSE, out.width='100%'}
markers <- list(
  "malignant" = CellType_metadata$ENSEMBL_ID[which(CellType_metadata$cell_class == "malignant")],
  "immune" = CellType_metadata$ENSEMBL_ID[which(CellType_metadata$cell_class == "immune")],
  "endothelium" = CellType_metadata$ENSEMBL_ID[which(CellType_metadata$cell_class == "endothelium")],
  "non-malignant" = CellType_metadata$ENSEMBL_ID[which(CellType_metadata$cell_class == "non-malignant")]
)

>>>>

- `nbins` is the number of bins for `AddModuleScore` to use. Its default value is 24, which matches Seurat's default value.
```{r}
MSigDB_score <- function(object, category, gs_name, name, nbin = 24) {
  set <- msigdbr(species = "human", category = category)
  set_list <- set %>%
    dplyr::filter(gs_name == gs_name) %>%
    dplyr::distinct(gs_name, gene_symbol, human_ensembl_gene) %>%
    as.data.frame()
  set_list <- list(set_list$human_ensembl_gene)
  suppressWarnings({
    object <- AddModuleScore(object, features = set_list, name = name, nbin = nbin)
  })
  return(object)
}
```

@@

### Cell cycle information
```{r cell_cycle, eval=!params$testing}
s.genes <- srat@assays$RNA@meta.data$gene_ids[srat@assays$RNA@meta.data$gene_symbol %in% cc.genes$s.genes]
g2m.genes <- srat@assays$RNA@meta.data$gene_ids[srat@assays$RNA@meta.data$gene_symbol %in% cc.genes$g2m.genes]
srat <- CellCycleScoring(srat, s.features = s.genes, g2m.features = g2m.genes, set.ident = FALSE, nbin = seurat_nbins)
```

```{r fig.width=20, fig.height=4, out.width='100%', eval=!params$testing}
visualize_metadata(srat, meta = "Phase", group.by = "seurat_clusters")
```

```{r fig.width=20, fig.height=2.5, out.width='100%', eval=!params$testing}
visualize_metadata(srat, meta = "S.Score", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "G2M.Score", group.by = "seurat_clusters")
```

@@

```{r fig.height=25, fig.width=20, message=FALSE, warning=FALSE, out.width='100%', eval=!params$testing}
markers <- list(
  "malignant" = CellType_metadata$ENSEMBL_ID[which(CellType_metadata$cell_class == "malignant")],
  "immune" = CellType_metadata$ENSEMBL_ID[which(CellType_metadata$cell_class == "immune")],
  "endothelium" = CellType_metadata$ENSEMBL_ID[which(CellType_metadata$cell_class == "endothelium")],
  "non-malignant" = CellType_metadata$ENSEMBL_ID[which(CellType_metadata$cell_class == "non-malignant")]
)
